### 2024-07-30 ms.qmd
Updates

```{r, models}
#| label: models
# Fitting the model and extraction of posteriors for both types of task and species using fit_m function (see func.r in R folder). The result everytime the function is used is a df with the posteriors of the model. The functions saves the model automatically in output/models; and when the parameter refit = FALSE then the posteriors are extracted from the model previously written instead of fitting the model again each time.
source(here("R", "func.R"))
# A) Associative task. Model formula: FC_associative ~ Associative_Trial*cort*temp + (1 + Associative_Trial|lizard_id)
## A.1) L. delicata
deli_asso_red <- fit_m("asso", "deli", "red", refit = FALSE)
write.csv(deli_asso_red, file= "./output/Checking/deli_asso_red.csv")
deli_asso_blue <- fit_m("asso", "deli", "blue", refit = FALSE)
write.csv(deli_asso_blue, file= "./output/Checking/deli_asso_blue.csv")
## A.2) L. guichenoti
guich_asso_red <- fit_m("asso", "guich", "red", refit = FALSE)
write.csv(guich_asso_red, file= "./output/Checking/guich_asso_red.csv")
guich_asso_blue <- fit_m("asso", "guich", "blue", refit = FALSE)
write.csv(guich_asso_blue, file= "./output/Checking/guich_asso_blue.csv")
# B) Reversal task. Model formula: FC_reversal ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)
## B.1) L. delicata
deli_rev_red <- fit_m("rev", "deli", "red", refit = FALSE)
write.csv(deli_rev_red, file= "./output/Checking/deli_rev_red.csv")
deli_rev_blue <- fit_m("rev", "deli", "blue", refit = FALSE)
write.csv(deli_rev_blue, file= "./output/Checking/deli_rev_blue.csv")
## B.2) L. guichenoti
guich_rev_red <- fit_m("rev", "guich", "red", refit = FALSE)
write.csv(guich_rev_red, file= "./output/Checking/guich_rev_red.csv")
guich_rev_blue <- fit_m("rev", "guich", "blue", refit = FALSE)
write.csv(guich_rev_blue, file= "./output/Checking/guich_rev_blue.csv")
```

@@

fig_prob_choice <- ggplot(df_prob, aes(x = Trial, y = Mean_Predicted_prob, color = Treatment)) +

@@

ggsave("./output/figures/fig_results_choice.png", plot=fig_results_choice, width = 25, height = 18, units = "cm", dpi = 600)
knitr::include_graphics("./output/figures/fig_results.png")

@@

####### A) Errors figure

@@

write.csv(data_fig, file= "./output/Checking/data_fig.csv")
write.csv(data_plot, file= "./output/Checking/data_plot.csv")

>>>>

```{r, models}
#| label: models
# Fitting the model and extraction of posteriors for both types of task and species using fit_m function (see func.r in R folder). The result everytime the function is used is a df with the posteriors of the model. The functions saves the model automatically in output/models; and when the parameter refit = FALSE then the posteriors are extracted from the model previously written instead of fitting the model again each time.
source(here("R", "func.R"))
# 
# df got from data_process.R
#
fchoice <- bf(choice_slope_mean + choice_slope_se ~ cort*temp)
ferrors <- bf(errors_slope_mean + errors_slope_se ~ cort*temp)
fROS <- bf(ROS ~ Mit_density + cort*temp)
#
refit <- FALSE
if(refit==TRUE){
  # Choice
  model_choice_2 <- brm(fchoice + fROS,
                data = clean_df,
                family = gaussian,
                chains = 4, cores = 4, iter = 8000, warmup = 2000, 
                control = list(adapt_delta = 0.99, max_treedepth = 12))
  # Errors
  model_errors_2 <- brm(ferrors + fROS,
                data = clean_df,
                family = gaussian,
                chains = 4, cores = 4, iter = 8000, warmup = 2000,
                control = list(adapt_delta = 0.99, max_treedepth = 12))
  # Write the models to two files
  saveRDS(model_choice_2, file = paste0(here("output/models/model_choice_2.rds")))
  saveRDS(model_errors_2, file = paste0(here("output/models/model_errors_2.rds")))
  } else {
    # Read the model from a file
    model_choice_2 <- readRDS(file = paste0(here("output/models/model_choice_2.rds")))
    model_errors_2 <- readRDS(file = paste0(here("output/models/model_errors_2.rds")))
} 
post_gen <- as_draws_df(model_errors_2)
write.csv(post_gen, file= "./output/Checking/post_gen.csv")
```

@@

fig_prob_choice <- ggplot(fig_choice_df, aes(x = Trial, y = Mean_Predicted_prob, color = Treatment)) +

@@

ggsave("./output/figures/fig_results_choice.png", plot=fig_results_choice, width = 25, height = 15, units = "cm", dpi = 600)

@@

####### B) Errors figure
## B.1) Plot the errors using data_spal
errors_df <- data_spal %>%
  mutate(Treatment = paste(cort, temp, sep = "-")) %>%
    mutate(Treatment = factor(Treatment,
      levels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")
    )) %>%
  group_by(day, Treatment) %>%
  summarise(
    mean_errors = mean(errors, na.rm = TRUE),
    sd_errors = sd(errors, na.rm = TRUE)
fig_errors <- ggplot(errors_df, aes(x = day, y = mean_errors, color = Treatment, fill = Treatment)) +
  geom_smooth(method = "lm", se = TRUE, linewidth = 1, alpha = 0.075) +
  scale_color_manual(values = c("CORT-Cold" = "#00008B", "Control-Cold" = "#68bde1", "CORT-Hot" = "#b50101", "Control-Hot" = "#fa927d")) +
  scale_fill_manual(values = c("CORT-Cold" = "darkblue", "Control-Cold" = "#68bde1", "CORT-Hot" = "#b50101", "Control-Hot" = "#fa927d")) +
  labs(y = "Mean amount of errors made", x = "Trial") +
## B.2) Make the the plot for the mean slope per treatment using the probability of choosing the correct feeder

@@

## B.3) Combine plots of probability and slopes to have the "choice" figure
fig_results_errors <- plot_grid(fig_errors, fig_slope_errors, nrow = 1) 
ggsave("./output/figures/fig_results_errors.png", plot=fig_results_errors, width = 25, height = 15, units = "cm", dpi = 600)

```{r, ROS-learning}
#| label: ROS-learning
tidy_post_fig_ROS <- post_gen %>%
  mutate(CORT_Cold = b_ROS_Intercept,
      Control_Cold = b_ROS_Intercept + b_ROS_cortControl,
      CORT_Hot = b_ROS_Intercept + b_ROS_tempHot,
      Control_Hot = b_ROS_Intercept + b_ROS_cortControl + b_ROS_tempHot + `b_ROS_cortControl:tempHot`) %>%
  select(CORT_Cold, Control_Cold, CORT_Hot, Control_Hot) %>%
  pivot_longer(cols = c(CORT_Cold, Control_Cold, CORT_Hot, Control_Hot), names_to = "Treatment", values_to = "ROS") %>%
  mutate(Treatment = factor(Treatment,
    levels = c("CORT_Cold", "Control_Cold", "CORT_Hot", "Control_Hot"),
    labels = c("CORT_Cold" = "CORT-Cold (n=20)",
              "Control_Cold" = "Control-Cold (n=20)",
              "CORT_Hot" = "CORT-Hot (n=18)",
              "Control_Hot" = "Control-Hot (n=20)")
  )) %>%
data_plot_ROS <- tidy_post_fig_ROS %>%
  group_by(Treatment) %>%
    Mean = mean(ROS),
    SD = sd(ROS),
    SE = sd(ROS)/sqrt(length(ROS))
write.csv(data_plot_ROS, here("output/Checking/data_plot_ROS.csv"))
fig_ROS <- ggplot(tidy_post_fig_ROS, aes(x = Treatment, y = ROS, fill = Treatment)) +
  geom_flat_violin(alpha = 0.5) +
  scale_fill_manual(values = c("CORT-Cold (n=20)"="#00008B", "Control-Cold (n=20)"="#68bde1", 
                    "CORT-Hot (n=18)"="#b50101", "Control-Hot (n=20)"="#fa927d")) +
  geom_point(data = data_plot_ROS, aes(y = Mean, x = Treatment), position = position_dodge(width = 0.75), color = "black", fill = "black", size = 3) +
  geom_segment(data = data_plot_ROS, aes(y = Mean - SD, yend = Mean + SD, x = Treatment, xend = Treatment), size = 1.5, color = "black") +
  geom_hline(yintercept = mean(data_plot_ROS$Mean), linetype = "dashed", color = "black") +
  ylim(min(tidy_post_fig_ROS$ROS), max(tidy_post_fig_ROS$ROS)) +
  coord_flip() +
  labs(y = "Slope estimates", x = "Treatments") +
  theme(plot.margin = margin(5.5, 5.5, 5.5, 5.5, "mm"),
    axis.text.y = element_blank(),   # Remove y-axis labels
    legend.position = "right",
    legend.title = element_text(size = 12, family = "Times"),
    legend.text = element_text(size = 11, family = "Times")
ggsave("./output/figures/fig_ROS.png", plot=fig_ROS, width = 15, height = 15, units = "cm", dpi = 600)
r_choice <- cor.test(clean_df$ROS, clean_df$choice_slope_mean, method = "pearson")
r_choice_text <- paste("r = ", round(r_choice$estimate, 2),
              " [", round(r_choice$conf.int[1], 2), ", ", round(r_choice$conf.int[2], 2), "]",
              sep = "")
r_errors <- cor.test(clean_df$ROS, clean_df$errors_slope_mean, method = "pearson")
r_errors_text <- paste("r = ", round(r_errors$estimate, 2),
              " [", round(r_errors$conf.int[1], 2), ", ", round(r_errors$conf.int[2], 2), "]",
              sep = "")
plot_ROS_choice <- ggplot(data = clean_df, aes(x = ROS, y = choice_slope_mean)) +
  geom_smooth(method = "lm", color = "#8D0001", fill = "#FFC3C3") +
  labs(y = "Estimated learning slope (Choice)", x = "ROS in medial cortex") +
  ) +
annotate("text", x = Inf, y = Inf, label = r_choice_text, 
           hjust = 1.05, vjust = 1.95, size = 4.5, color = "#8D0001")
plot_ROS_errors <- ggplot(data = clean_df, aes(x = ROS, y = errors_slope_mean)) +
  geom_smooth(method = "lm", color = "#8D0001", fill = "#FFC3C3") +
  labs(y = "Estimated learning slope (Errors)", x = "ROS in medial cortex") +
  ) +
annotate("text", x = Inf, y = Inf, label = r_errors_text, 
           hjust = 1.05, vjust = 1.95, size = 4.5, color = "#8D0001")
fig_ROS_learning <- plot_grid(plot_ROS_choice, plot_ROS_errors, nrow = 1) 
ggsave("./output/figures/fig_ROS_learning.png", plot=fig_ROS_learning, width = 25, height = 15, units = "cm", dpi = 600)
